---
title: Maxime Dahirel
subtitle: (they/he)
format: 
    pdf:
      keep-tex: false
      include-in-header: 
       - "cv-header.tex"
      toc: false
      toc-depth:  2
      code-block-bg: light
      linkcolor: links
      urlcolor: links
      fontsize: 10pt
      geometry:
        - a4paper
        - left=20mm
        - top=20mm
        - bottom=20mm
        - right=65mm
        - marginparwidth=50mm
        - marginparsep=8mm
---
```{r}
#| echo: false
#| message: false
library(tidyverse)
library(glue)
library(ggtext)
library(commonmark)
library(here)
source('./R/parsing_functions.R')
source('./R/get_data.R')
```

::: {.column-margin}

`\vspace{-12em}`{=latex}

## Info {#info}

{{< fa envelope >}} maxime.dahirel\@ugent.be\
{{< fa envelope >}} maxime.dahirel\@yahoo.fr\
{{< fa at >}} [\@mdahirel.bsky.social](https://bsky.app/profile/mdahirel.bsky.social)\
{{< fa at >}} [\@mdahirel\@mastodon.social](https://mastodon.social/@mdahirel)\
{{< fa brands github >}} [\@mdahirel](https://github.com/mdahirel)\
{{< fa home >}} [mdahirel.github.io/](https://mdahirel.github.io/)\
{{< fa orcid >}} [0000-0001-8077-7765](https://orcid.org/0000-0001-8077-7765)

Member of the British Ecological Society

## Key skills {#skills}

### {{< fa spider >}} Invertebrate zoology {#taxa}

(primarily land snails and spiders)  
**Rearing**  
**Trait measurements**  
**Behavioural observations**   
**Field sampling methods**  
**Species ID** (Western Europe)  

### {{< fa comment >}} Languages {#languages}

```{r}
#| echo: false
#| fig-height: 2.4
language_skills |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```

### {{< fa code >}} Programming languages {#coding}

```{r}
#| echo: false
#| fig-height: 1.6
coding |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```
### {{< fa chart-line >}} Data science and statistics {#stats}

**Version control with Git & GitHub**  
**Quarto/RMarkdown**  
**Shiny apps development** (offline)  
**Bayesian & frequentist statistics**  
Linear models and extensions
(Any and all combinations of generalized, mixed/hierarchical, additive, non-linear, or multi-response)  
**Ordination and classification methods**  
**Advanced data visualisation**  
**Spatial data science & GIS**  
**Individual-based modelling**

### {{< fa laptop >}} Other software {#software}

```{r}
#| echo: false
#| fig-height: 2.4
software |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```
:::

My researches are mostly split along two linked axes: 

- **urban biodiversity, ecology and evolution**, with a focus on the role of trait variation in explaining species' ability (or inability) to persist in cities  

- **dispersal** as a bridge between ecological and evolutionary dynamics.

I develop these research themes using a combination of lab and outdoor experiments, monitoring in naturalistic contexts and individual-based models. A key aspect of my work is the use of advanced statistical and data science methods that accurately reflect the complexity of the natural systems I study.

**To go directly to the list of publications [click here](#publications)**

## Most recent position {#lastjob}

```{r}
#| echo: false
#| output: asis
print_position(position_data, 'current-job')
```

## Previous positions {#jobs}

```{r}
#| echo: false
#| output: asis
print_position(position_data, 'previous-positions')
```

## Teaching experience {#teaching}

```{r}
#| echo: false
#| output: asis
print_position(position_data, 'teaching-positions')
```

### Courses taught or co-taught in these positions include:  

| **Statistics and data science** (lectures and practical)  
|      Advanced R for data analysis (1st year of MSc) ~ 20h  
|      Statistical tools and experimental design (2nd year of BSc to 1st year of MSc) ~ 230h  

| **Ecology** (lab and field)   
|      General ecology (1st year of BSc) ~ 80h  
|      Community ecology (3rd year of BSc and 1st year of MSc) ~ 42h  
|      Spatial ecology (movement ecology; 1st year of MSc) ~ 4h  
|      Ecological bases of vegetal production (3rd year of BSc) ~ 12h  
|      Initiation to GIS (2nd year of BSc) ~ 4h  

| **Zoology**  (lab and field)  
|      Introduction to the diversity of life (1st year of BSc) ~ 30h  
|      Entomology (3rd year of BSc) ~ 40h  
|      Physiology of nutrition, development, growth (3rd year of BSc) ~ 6h  

## Mentoring experience {#mentoring}

:::aside
See list of students for current year [here](https://mdahirel.github.io/post/people/)
:::

| **Co-supervision of 1 PhD student**  

|      \small{{< fa calendar >}} 2020 - 2023 \normalsize
|      - Experimental evolution  
|      - Data synthesis and individual-based modelling  

| **Supervision of 13 MSc students, 1st or 2nd year, and 7 BSc students (1 to 6 months projects)**  

|      \small{{< fa calendar >}} 2012 - present \normalsize
|      - Urban ecology and dispersal ecology 
|      - Field and lab studies
|      - Data synthesis and individual-based modelling  

## Research funding {#money}

```{r}
#| echo: false
#| output: asis
print_funding(funding, 'research')
```

## Selected science communication {#scicomm}

:::aside 
{{< fa newspaper >}} Research I have participated in has also been featured by various press outlets including the [RTBF](https://www.rtbf.be/info/societe/detail_les-animaux-changent-de-taille-quand-ils-vivent-en-ville?id=9925810), [De Standaard](https://www.standaard.be/cnt/dmf20180402_03441454), [Scientific American](https://www.scientificamerican.com/podcast/episode/city-life-favors-downsized-invertebrates/), [Le Temps](https://www.letemps.ch/sciences/lurbanisation-un-probleme-taille), as well as local journals and television channels.
:::

**Invited speaker, Ateliers À propos**

|    \small{{< fa calendar >}} 2022 \normalsize  
|    Online science workshop (targeted to 6-12 year olds): invited for a session on snail biology, urban ecology (in French)

**[Contributor to the Life in the City : Evolution in an Urbanizing World blog](https://urbanevolution-litc.com/)**

|    \small{{< fa calendar >}} 2018-2019 \normalsize  
|    Discussions of current topics and articles in urban ecology and evolution

## Service {#service}

**Referee for various journals and outlets** 

including *Proceedings of the Royal Society B*, *Functional Ecology*, *Journal of Animal Ecology*, *Oikos*, *PCI Ecology*, *Animal Behaviour*… 

**Member of the Grant Review College of the British Ecological Society**

Reviewing Research and Outreach Grant applications (typically 4 to 6 / year)

**PhD students representative to the Advisory Board of the research unit**

|    \small {{< fa calendar >}} 2012-2014 \normalsize  
|    University of Rennes 1, ECOBIO research unit

## Publications {#publications}

```{r import_info}
#| echo: false

preprints <- filter(articles,section=="preprint") |> 
  arrange(-year)
published <- filter(articles, section=="peer-reviewed") |> 
  arrange(-year)
reports <- filter(articles, section=="report") |> 
  arrange(-year)
```

## Preprints (`r length(preprints$title)`) {#preprints}

```{r results='asis'}
#| echo: false

print_papers(preprints)
```

## Peer-reviewed publications (`r length(published$title)`) {#peer-reviewed}

```{r results='asis'}
#| echo: false

print_papers(published)
```

## Other publicly available reports (`r length(reports$title)`) {#reports}

```{r results='asis'}
#| echo: false

print_papers(reports)
```

## Communications in conferences {#conferences}

:::aside 
(Talks or posters as non-presenting author not included)
:::

## Talks (`r dim(filter(talks_and_posters, section=="talk"))[1]`) {#talks}

```{r results='asis'}
#| echo: false

print_meetings(talks_and_posters|> filter(section=='talk'))
```

## Posters (`r dim(filter(talks_and_posters, section=="poster"))[1]`) {#posters}

```{r results='asis'}
#| echo: false

print_meetings(talks_and_posters|> filter(section=='poster'))
```

## Workshops {#workshops} 

```{r results='asis'}
#| echo: false

print_meetings(talks_and_posters|> filter(section=='workshop'))
```

## Predoctoral education {#predoc_ed} 

```{r}
#| echo: false
#| output: asis
print_position(education, 'diploma')
```

## References

```{r results='asis'}
#| echo: false

print_references(references)
```



::: {.aside}
`\vspace{90em}`{=latex}

Made with [Quarto](https://quarto.org/)  
Code on [GitHub](https://github.com/mdahirel/cv)  
Icons from [Font Awesome](https://fontawesome.com/)  
CV last updated on `r Sys.Date()`
:::
