---
title: Maxime Dahirel
subtitle: Quantitative ecologist, data scientist
format: 
    pdf:
      keep-tex: false
      include-in-header: 
       - "cv-header.tex"
      toc: false
      toc-depth:  2
      code-block-bg: light
      linkcolor: links
      urlcolor: links
      fontsize: 10pt
      geometry:
        - a4paper
        - left=20mm
        - top=20mm
        - bottom=20mm
        - right=65mm
        - marginparwidth=50mm
        - marginparsep=8mm
---
```{r}
#| echo: false
#| message: false
library(tidyverse)
library(glue)
library(ggtext)
library(commonmark)
library(here)
source('./R/parsing_functions.R')
source('./R/get_data.R')
```

```{r import_info}
#| echo: false

preprints <- filter(articles,section=="preprint") |> 
  arrange(-year)
published <- filter(articles, section=="peer-reviewed") |> 
  arrange(-year)
```

::: {.column-margin}

`\vspace{-12em}`{=latex}

### {{< fa info >}} Info {#info}

{{< fa envelope >}} maxime.dahirel\@ugent.be\
{{< fa envelope >}} maxime.dahirel\@yahoo.fr\
{{< fa brands github >}} [github.com/mdahirel](https://github.com/mdahirel)\
{{< fa home >}} [mdahirel.github.io/](https://mdahirel.github.io/)\

### {{< fa comment >}} Languages {#languages}

```{r}
#| echo: false
#| fig-height: 2.4
language_skills |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```

### {{< fa code >}} Programming languages {#coding}

```{r}
#| echo: false
#| fig-height: 1.6
coding |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```
### {{< fa chart-line >}} Data science and statistics {#stats}

**Version control with Git & GitHub**  
**Quarto/RMarkdown**  
**Bayesian & frequentist statistics**  
Linear models and extensions
(Any and all combinations of generalized, mixed, non-linear, or multivariate)  
Ordination and classification methods  
...  
**Spatial data science & GIS**  

### {{< fa laptop >}} Other software {#software}

```{r}
#| echo: false
#| fig-height: 2.4
software |> 
  mutate(skill=fct_reorder(skill,level)) |> 
  build_skill_bars()
```
:::

## Highlights {#highlights}

- 12 years of experience in statistics, experimental and observational study design applied to ecology
- Recognised expert in animal behaviour and urban biodiversity/ecology
- Expertise in R-based data science workflows
- Expertise in classical and Bayesian statistics
- Author of `r length(published$title)` peer-reviewed scientific papers, with about 3/4 of those in a major role: lead or senior author, data analyst or research designer
- Experienced in research supervising roles, funding acquisition from local to EU level, project management

## Most recent position {#lastjob}

```{r}
#| echo: false
#| output: asis
print_position(position_data, 'current-job')
```

## Previous positions {#jobs}

```{r}
#| echo: false
#| output: asis
print_position(position_data, 'previous-positions')
```

TO REFORMAT, + ADD KEY SKILLS

## Education {#education}

**PhD**

**Master**

**Bachelor**

::: {.aside}
Made with [Quarto](https://quarto.org/)  
Code on [GitHub](https://github.com/mdahirel/cv)  
last updated on `r Sys.Date()`
:::
